%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer Intern, Morse Corp, Cambridge MA}{January 2025 - Present}
{\vspace{-\baselineskip}}{}
\resumeItemListStart
\resumeItem { Built core infrastructure for data analysis pipelines aimed at algorithmic testing and evaluation of object detection models. }
\resumeItem { Deployed data integration pipelines and containerized automation tools for accelerating model testing and metric turnaround. }
\resumeItem { Created tools for processing model GPU/CPU performance and inferencing for visualizations and bounding box overlaying. }
\resumeItemListEnd

\resumeSubheading
{Technical Lead, Generate Product Development Studio, Boston MA}{September 2024 - April 2025}
{\vspace{-\baselineskip}}{}
\resumeItemListStart
\resumeItem { Led \textbf{7} software engineers, engineering \textbf{CI/CD} pipelines to containerize deployments, automate builds and integration tests. }
\resumeItem{
	Designed a distributed web server that supported multimedia compression/serving, scheduler services, and client-server auth.
}
\resumeItem{
	Continously promoted learning through test driven development, pair-programming, workshops, and agile methodologies.
}
\resumeItemListEnd

\resumeSubheading
{Lead Lab TA for CS2500, Khoury College, Boston, MA}{September 2024 - December 2024}
{\vspace{-\baselineskip}}{}
\resumeItemListStart
\resumeItem { Helped \textbf{600+} students by teaching systematic program design with topics including structural recursion and accumulators. }
\resumeItem { Held weekly lab sessions for \textbf{30+} students, reviewing course fundamentals, design concepts/paradigms, and exam reviews. }
\resumeItem { Led engaging office hours, enabling students to proactively reason about self-referential data, and graph/tree algorithms. }
\resumeItemListEnd

\resumeSubheading
{Software Development Intern, Spill Center, Hudson, MA}{January 2024 -- August 2024}
{\vspace{-\baselineskip}}{}
\resumeItemListStart
\resumeItem { Tracked over \textbf{800,000} cargo tank facilities and tanks by architecting a centralized web application for cargo tank life events. }
\resumeItem { Monitored \textbf{10,000+} incidents and alert groups by implementing a geospatial alert service through PostGIS spatial queries. }
\resumeItem { Utilized database schemas which mapped regulatory reports to geographic areas, enabling for more detailed incident reports. }
\resumeItemListEnd

\resumeSubHeadingListEnd
