%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Dearly} $|$ \emph{TypeScript, React-Native, Docker, AWS S3 and Lambda, Nix, SQL}}    {}
\resumeItemListStart
\resumeItem{Dearly is a private family-sharing app that bridges generational gaps and makes staying connected easier and meaningful.}
\resumeItem{Created CI/CD pipelines that rigorously ran over \textbf{500} integration tests as well as containerized and deployed docker images. }
\resumeItem{Delivered a type-safe \textbf{REST} backend using type generation and architected protocol abstractions over \textbf{AWS S3} and \textbf{Lambda}.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Bazaar} $|$ \emph{Java, Maven, Bash, Gson}}    {}
\resumeItemListStart
\resumeItem { Created a distributed trading card game with functional-style Java, where player mechanisms connect over \textbf{TCP} protocols.}
\resumeItem { Developed a tree-search algorithm that efficiently searched through millions of candidates using DFS and data accumulators.}
\resumeItem { Created a robust server component which protected itself from DOS attacks and malformed JSON responses from clients.
}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{TankFax} $|$ \emph{Vue.js, Nuxt.js, TypeScript, MongoDB}}    {}
\resumeItemListStart
\resumeItem { TankFax aggregates the life-cycle details of cargo tanks to allow informed decisions on over \textbf{800,000} cargo tanks.}
\resumeItem{ Built dynamic CRUD endpoints to support database transactions and created realistic data-gen scripts for testing scalability. }
\resumeItem { Designed structurally recursive user dashboards, tank report pages, and stored their representations using database schemas.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Snapper} $|$ \emph{React-Native, TypeScript, MongoDB, AWS}}    {}
\resumeItemListStart
\resumeItem { Snapper is a gamified social platform for divers and marine enthusiasts alike to learn more about the marine life around them.}
\resumeItem { Developed an S3 protocol where images  would be parsed and uploaded or deleted from their respective S3 buckets.
}
\resumeItem { Developed paginated endpoints for users, dives, and fish collections. Utilized full-text search to support fuzzy finding. }
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Couplet} $|$ \emph{React-Native, TypeScript, Golang, PostgreSQL}}    {}
\resumeItemListStart
\resumeItem{ Couplet is a dating app focusing on meaningful connections through shared interests in local events and activities. }
\resumeItem { Implemented global state management through redux to allow sharing of user state across the onboarding flow. }
\resumeItem{ Developed CRUD API to support user/event creation, user/event recommendations, and user matching algorithms. }
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Chinese Language Table} $|$ \emph{React.js, TypeScript, Next.js, MongoDB, AWS}}    {}
\resumeItemListStart
\resumeItem {The Chinese Language Table website is an extension of the student-driven Northeastern club, focusing on learning Chinese. }
\resumeItem{ Designed and implemented the user interface for navigating the landing page, club events, news, and login/signup pages.  }
\resumeItem{ Architected a REST backend, handling CRUD operations for club events, Google OAuth, and storing files with AWS S3. }
\resumeItemListEnd

\resumeSubHeadingListEnd
